% arara: xelatex
% arara: xelatex
% arara: xelatex


% options:
% thesis=B bachelor's thesis
% thesis=M master's thesis
% czech thesis in Czech language
% english thesis in English language
% hidelinks remove colour boxes around hyperlinks

\documentclass[thesis=B,english]{FITthesis}[2019/12/23]

%\usepackage[utf8]{inputenc} % LaTeX source encoded as UTF-8
% \usepackage[latin2]{inputenc} % LaTeX source encoded as ISO-8859-2
% \usepackage[cp1250]{inputenc} % LaTeX source encoded as Windows-1250

% \usepackage{subfig} %subfigures
% \usepackage{amsmath} %advanced maths
% \usepackage{amssymb} %additional math symbols

\usepackage{dirtree} %directory tree visualisation

% % list of acronyms
% \usepackage[acronym,nonumberlist,toc,numberedsection=autolabel]{glossaries}
% \iflanguage{czech}{\renewcommand*{\acronymname}{Seznam pou{\v z}it{\' y}ch zkratek}}{}
% \makeglossaries

% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % 
% EDIT THIS
% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % 

\department{Department of Applied Mathematics}
\title{Detection of defects in X-Ray images using Neural Networks}
\authorGN{Matúš} %author's given name/names
\authorFN{Botek} %author's surname
\author{Matúš Botek} %author's name without academic degrees
\authorWithDegrees{Matúš Botek} %author's name with academic degrees
\supervisor{Ing. Jakub Žitný}
\acknowledgements{I would like to thank my supervisor, Ing. Jakub Žitný, for his valuable insight and guidance during the writing process of my thesis. Furthermore, I would also like to thank my family and friends, who supported me the whole time.}
\abstractEN{Summarize the contents and contribution of your work in a few sentences in English language.}
\abstractCS{V n{\v e}kolika v{\v e}t{\' a}ch shr{\v n}te obsah a p{\v r}{\' i}nos t{\' e}to pr{\' a}ce v {\v c}esk{\' e}m jazyce.}
\placeForDeclarationOfAuthenticity{Prague}
\keywordsCS{konvoluční neurónové sítě, rentgenové snímky, MURA, klasifikace, předspracování dat, TensorFlow, Keras}
\keywordsEN{convolutional neural networks, X-Ray images, MURA, classification, data preprocessing, TensorFlow, Keras}
\declarationOfAuthenticityOption{1} %select as appropriate, according to the desired license (integer 1-6)
% \website{http://site.example/thesis} %optional thesis URL


\begin{document}

% \newacronym{CVUT}{{\v C}VUT}{{\v C}esk{\' e} vysok{\' e} u{\v c}en{\' i} technick{\' e} v Praze}
% \newacronym{FIT}{FIT}{Fakulta informa{\v c}n{\' i}ch technologi{\' i}}

\setsecnumdepth{part}
\chapter{Introduction}



\setsecnumdepth{all}
\chapter{Medical imaging}


\chapter{Machine learning}


\chapter{State of the Art}


\chapter{Implementation and design}
This chapter describes major parts of my implementation, including chosen technologies. It also introduces the dataset used in all experiments.

\section{Technologies}
The whole implementation is written in Python. It has high code readability and strong community support. There are many powerful libraries focused on ML for Python, which make it one of the most popular programming languages when it comes to ML tasks.

Most important libraries


\section{Dataset}

\chapter{Experiments}

\setsecnumdepth{part}
\chapter{Conclusion}

\bibliographystyle{iso690.bst}
\bibliography{ref}

\setsecnumdepth{all}
\appendix

\chapter{Acronyms}
% \printglossaries
\begin{description}
	\item[CLAHE] Contrast limited adaptive histogram equalization
	\item[CNN] Convolutional neural network
	\item[MURA] Musculoskeletal radiographs dataset
\end{description}


\chapter{Contents of enclosed CD}

%change appropriately

\begin{figure}
	\dirtree{%
		.1 readme.txt\DTcomment{the file with CD contents description}.
		.1 src\DTcomment{the directory of source codes}.
		.2 wbdcm\DTcomment{implementation sources}.
		.2 thesis\DTcomment{the directory of \LaTeX{} source codes of the thesis}.
		.1 text\DTcomment{the thesis text directory}.
		.2 thesis.pdf\DTcomment{the thesis text in PDF format}.
		.2 thesis.ps\DTcomment{the thesis text in PS format}.
	}
\end{figure}

\end{document}
